Towards a Complete Model of Mutation Selection Balance in Humans

### 2023-02-19 manuscript/manuscript.tex
ms notes
minor ms changes

@@

@@

Our $B$ is,

\begin{align}
  B = \frac{1}{2N} \sum_{t=0}^\infty \prod_{i=0}^t \left(1 - \frac{1}{2N_e(i)}\right).
\end{align}

This sum takes many terms to converge, which makes calculating the $B$ between
each focal neutral site and segment intractably slow (even when the equilibrium
$\widetilde{V}$ for the segment pre-calculated). We approximate this in the
following way for faster numerical calculations. Let $g(t) = \prod_{i=0}^t (1 -
\nicefrac{1}{2N_e(i)})$. Then, taking the first-order series expansion around
the logarithm of the terms and approximating the sum with an integral,

\begin{align}
  g(t) &\approx \exp\left(- \frac{1}{2N} \int_0^t \exp\left(\frac{V}{2} Q(x)^2 \right) dx \right) 
       %&\approx \exp\left(- \int_0^t \frac{\exp\left(\frac{V}{2} Q(i)^2\right)}{2N}  dx \right)
\end{align}

$B$ is the case of $\lim b \to \infty$ for $B(b)$. Approximating the sum in
$B(b)$ with an integral,

\begin{align}
  B(b) &= \int_0^b \exp\left(- \frac{1}{2N} \int_0^t \exp\left(\frac{V}{2} Q(x)^2 \right) dx \right) dt \\
       %&\approx \exp\left(- \int_0^t \frac{\exp\left(\frac{V}{2} Q(i)^2\right)}{2N}  dx \right)
\end{align}

Now, let $z = \log(t)$, then

\begin{align}
  B(w) &= \int_0^w \exp\left(- \frac{1}{2N} \int_0^{\log(z)} \exp\left(\frac{V}{2} Q(x)^2 \right) dx \right) \exp(t) dz \\
       %&\approx \exp\left(- \int_0^t \frac{\exp\left(\frac{V}{2} Q(i)^2\right)}{2N}  dx \right)
\end{align}

>>>>

Note on the importance of selection in humans.
NOTE about the importance of calibration

@@

- need for coalescent simulations with reduced $N_e$ along the genome.

@@

\subsection*{Optimization}

Optimization in non-linear regression is notoriously difficult both in general
(Bates) and in the specific problem of estimating the effects of genome-wide
selection \parencite{Murphy2022-sj}. We experimented with a variety of global
and local optimization approaches and parameterizations, but found that
